%% LaTeX2e class for student theses
%% sections/content.tex
%% 
%% Karlsruhe Institute of Technology
%% Institute for Program Structures and Data Organization
%% Chair for Software Design and Quality (SDQ)
%%
%% Dr.-Ing. Erik Burger
%% burger@kit.edu
%%
%% Version 1.3.5, 2020-06-26

\chapter{Fundamentals}
\label{ch:Fundamentals}

Topics:
\begin{itemize}[noitemsep,nolistsep]
	\item multiagent/multibody Systems (MAS).
	\begin{itemize}[noitemsep,nolistsep]
		\item MAS Reinforcement Learning
		\begin{itemize}[noitemsep,nolistsep]
			\item They use stochastic games (Markov Games) as generalization of Markov Decision Processes.
		\end{itemize}
		\item Hierarchical MAS, Hierarchical Reinforcement Learning for MAS.
		\item MAS with Cooperation and Competition.
		\item Particle Swarms (nicht so meins).
		\item Problems:
		\begin{itemize}[noitemsep,nolistsep]
			\item MAS Movement Problems (Potential Fields).
			\item ? using MAS for Moving a Multi-Legged Robot (Spider-like) with a navigation problem design as a hierarchical MAS?
			\item Path Planning Navigation with Heterogeneous Agents? 
			\item MAS Task Problems: Rendezvous, Pursuit Evasion (Single and one Evader) (Boid?), (MAS - Deep Reinforcement Learning for Robot Swarms - 2019 - KIT)
			\item Multi-Agent Path Finding (MAPF). Scalability for this: For fixed space they get into each others way.
			\item Collective Foraging: (Ants-kinda). Problem when communication only happens in an area, use local information exchange groups. Information Transfer. (MAS - Swarm Intelligence - 2020), Preferential Foraging (MAS - Swarm Intelligence - 2018 - p.289)
			\item Coverage: Multi-robot Information Gathering / Scouting. (MAS - Swarm Intelligence - 2020), Pattern Formation (MAS - Swarm Intelligence - 2016 - p.14)
			\item Coalition: Heterogeneous Group of Agents. They have different skills / attrributes that affect the environment. Like an Ant Caste System? Some Agents have better sensors? Only some agents have some sensors? What if the specialization is taken to the extreme? (MAS - Swarm Intelligence - 2020). Limited Visibility Sensors (MAS - Swarm Intelligence - 2018 - p.56). Going from a homogeneous group of agents, to randomized specialities, to extrem specializations. How does it change? Mixed with an Hierarchical Approach? They need to find groups to work together? Some are fast (but cannot see much, there is an insect that cannot see while running), Some have good sensors. Communication range? Genetic Diversity, Task-Allocation and Task-Switching (MAS - Swarm Intelligence - 2016 - p.109)
			\item Collective Gradient Perception: Using Abilities of other Agents to take advantage of the whole group. (Flocking) (MAS - Swarm Intelligence - 2020)
			\item Indirect Communication through changing states in the environment (birds transport something via cable). Also like using Pheromone Trails (Quality-Sensitive Foraging through virtual pheromone trails). (MAS - Swarm Intelligence - 2018 - p.15 - p.147)
			\item Control Architecture: Behavior Trees, FSM. (MAS - Swarm Intelligence - 2018 - p.42)
			\item Maze-Like Environment with Ant Algorithms (MAS - Swarm Intelligence - 2018 - p.162) 
			\item Search and Rescue? (Kinda like Foraging?)
			\item Disruption: Disrupting Aspects of the Swarm and how they react to it, Swarm Attack: (MAS - Swarm Intelligence - 2018 - p.225), Coherence of Collective Decision Making (MAS - Swarm Intelligence - 2018 - p.264)
			\item Evolutionary Systems: NEAT (MAS - Swarm Intelligence - 2012 - p.98)
		\end{itemize}
		\item Graph-Based Visualisation for MAS. (MAS - Swarm Intelligence - 2010). How do you visualize them?
		\item Adding new Agents to the mix, can you use transfer learning?
		\item Adaptive Learning for MAS?
		\item Control System: Either fully self-organizing or completely centralized. Hybrid Control of Swarms (MAS - Swarm Intelligence - 2018 - p.69)
		\item Simulation of MAS: ARGoS
		\item Best-of-n Problem: Swarm selects best option out of n alternatives. (MAS - Swarm Intelligence - 2018 - p.251)
		\item Sensory Errors for Foraging, Dynamic Task Partiotioning (MAS - Swarm Intelligence - 2016 - p.124), Task Partitioning Problem (MAS - Swarm Intelligence - 2012 - p.122)
		\item Task Hierarchy, Multi-Objective
		\item Random Walks as a search strategy (MAS - Swarm Intelligence - 2016 - p.196)
		
	\end{itemize}
	\item Ant-Colony-Optimization (ACO)
	\begin{itemize}[noitemsep,nolistsep]
		\item ACO for learning.
		\item ACO for classification: (MAS - Swarm Intelligence - 2016 - p.64)
	\end{itemize}
	\item General RTS AI Approaches.
	\begin{itemize}[noitemsep,nolistsep]
		\item FSM
		\item Behavior Trees
		\item GOAP
	\end{itemize}
	\item RTS-Learning
	\begin{itemize}[noitemsep,nolistsep]
		\item Reinforcement Learning
		\item Learning Probabilistic Models
		\item CNN
	\end{itemize}
\end{itemize}
